A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}. Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations. Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case. While Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case. The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.

Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases. The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case is obtainable with HOSVD for a 3-D model. Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model which is in Figure~\ref{fig:3D_PermFields}(b). When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable. For example:
\begin{enumerate}
\item The model retains heterogeneity within each region
\item A single realization will be obtained for the same upgrid resolution
  \item The correlation to local heterogeniety in the base case is maintained
\end{enumerate}

>>>>

\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}. Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations wich contain 2019 (BaseCase)and 303 tetrahedral \PNDG[1]{1} element-pairs (3-D PCA using HOSVD). The number of elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.

Figure~\ref{fig:3D_PermFields} shows the permeability distribution for the 3-D cases. The aim here is to show that the PCA-LinReg model, previously obtained with SVD for the 2-D case, can also be obtainable with HOSVD for a 3-D model. Therefore, we only concentrate on one upscaling case for the 3-D model, that is the PCA (using HOSVD) LinReg Model (Fig.~\ref{fig:3D_PermFields}b). When this model is compared to the base case, Figure~\ref{fig:3D_PermFields}(a), the same advantages of PCA-LinReg model from the 2-D case are observable. For example:
\begin{enumerate}
\item The model retains heterogeneity within each region
\item A single realization will be obtained for the same upgrid resolution
  \item The correlation to local heterogeniety in the base case is maintained
\end{enumerate}
